paper1_results_figs_slimmed_50_rr

### 2016-06-27 inst/documents/paper1_results_figs_slimmed_50_rr.Rmd
improve plot

```{r, eval=TRUE, echo=FALSE, warning=FALSE, fig.height=3.5}

@@

@@

    cat("A)")

    print( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) + 
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = element_text(angle = 45,hjust = 1, vjust = 1)) +
             geom_hline(yintercept = 0, linetype=3) +
             #theme_bw() +
             ylim(-1,1) +
             xlab(NULL)
          )

@@

    cat("B)")

    print( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) + 
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = element_text(angle = 45,hjust = 1, vjust = 1)) +
             geom_hline(yintercept = 0, linetype=3) +
             #theme_bw() +
             ylim(-1,1) +
             xlab(NULL)
          )

>>>>

@@

  #list to put plots in for cowplot
  plotlist <- list(2)

@@

    #cat("A)")

    plotlist[[1]] <- ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) + 
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = element_blank()) +
             geom_hline(yintercept = 0, linetype=3) +
             ggtitle(paste("A) Mixture minus sequential")) +
             ylim(-1,1) +
             xlab(NULL)

@@

    #cat("B)")

    plotlist[[2]] <- ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) + 
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = element_text(angle = 45,hjust = 1, vjust = 1)) +
             geom_hline(yintercept = 0, linetype=3) +
             ggtitle(paste("B) Adaptive minus sequential")) +
             ylim(-1,1) +
             xlab(NULL)

  plot_grid( plotlist[[1]],plotlist[[2]],ncol=1, rel_heights=c(1,1.6))
